Strong Gravitational Lensing Finding Challenge

### 2017-03-08 paper.tex
Edit.

\subsection{YattaLens Lite (Alessandro Sonnenfeld)}
YattaLensLite is a simpler version of the algorithm YattaLens (Sonnenfeld et al. in prep.), modified to meet the time constraints of the challenge.
YattaLensLite subtracts a model surface brightness profile describing the lens galaxy from the $g$-band image, then runs SExtractor to detect tangentially elongated or ring-shaped objects, which are interpreted as lensed images.
In the ground-based challenge, the model lens surface brightness profile is obtained by taking a rescaled version of the $i$-band image.
The difference in color between lens and source usually allows the lensed images to still be detectable after the lens subtraction process.
However in order to avoid subtracting off the lensed images in systems with similar colors between lens source, we radially truncate the model lens surface brightness.
at the smallest radius between the position where the surface brightness is comparable to the sky background level or the position of a positive radial gradient in surface brightness, if detected.

>>>>

\subsection{YattaLens Lite (Alessandro Sonnenfeld)}
YattaLensLite is a simpler version of the algorithm YattaLens \citep{Sonnenfeld17}, modified to meet the time constraints of the challenge.
YattaLensLite subtracts a model surface brightness profile describing the lens galaxy from the $g$-band image, then runs SExtractor to detect tangentially elongated or ring-shaped objects, which are interpreted as lensed images.
In the ground-based challenge, the model lens surface brightness profile is obtained by taking a rescaled version of the $i$-band image.
The difference in color between lens and source usually allows the lensed images to still be detectable after the lens subtraction process.
However in order to avoid subtracting off the lensed images in systems with similar colors between lens source, we radially truncate the model lens surface brightness.
at the smallest radius between the position where the surface brightness is comparable to the sky background level or the position of a positive radial gradient in surface brightness, if detected.
